Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-15 paper/tv.tex
m

\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

\usepackage{tikz}
\usepackage{xcolor}
\usepackage[thicklines]{cancel}
\renewcommand{\CancelColor}{\color{lightgray}}

@@

@@

Looking at the second sub-tree, in step \textcircled{5}, \code{t_L} and \code{t_R} are firstly split 
into \code{t_L^1{+}t_L^2} and \code{t_R^1{+}t_R^2}. 
Then in step {\textcircled{6}, 
\code{\{A\} \mysharp  t_L^1} together with \code{\{A\} \mysharp  t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
%, also
%are unified as new constraint \code{t_L^1{=}t_R^1}.
In step {\textcircled{7}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
%one in
%step \code{\textcircled{1}}, 
Hence we apply the rule \code{[REOCCUR]} to prove it with a succeed side constraints entailment: \code{\textcolor {
      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    }\Rightarrow
    \textcolor {darkred}{t_R{<}4} }. 
%Since the structure of terms \code{t_L^2, t_L} and \code{t_R^2, t_R} are isomorphic,
%we will need to unify \code{t_L^2} and \code{t_R^2} in order to get enough
%time constraints. And in step \code{\textcircled{5}} we prove the proposition to
%be true.

@@

\hypo{
  \code{
    \textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True} \qquad
    \epsilon \CONTAIN \epsilon
  }
}

\infer[dashed]1[{\textcircled{4}\siderule{\codeme{[PROVE]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge \epsilon \CONTAIN
    \textcolor {darkred}{True} \wedge \epsilon
  }
}

\infer[dashed]1[{\textcircled{3}\siderule{\codeme{[Normalisation]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge \cancel{\{B\}} \CONTAIN
    \textcolor {darkred}{True} \wedge \cancel{ \epsilon \cdot \{B\}}
  }
}

\infer[dashed]1[{\textcircled{2}\siderule{\codeme{[UNFOLD]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
  }
}
\hypo{(\code{II})}

\infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {darkred}{t_L{<}3}  \wedge  \{A\}^\star \mysharp  t_L  \cdot  \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4}  \wedge  \{A\}^\star \mysharp  t_R  \cdot  \{B\}
  }
}

\infer[dashed]2[{\textcircled{1}\siderule{\codeme{[OR\text{-}LHS]}}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
    \vee \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
  }
}
\end{prooftree}}
\\~\\

\hline \\
\code{(II):} \qquad 
{\begin{prooftree}
\hypo{
  \code{
    \textcolor {
      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    } \Rightarrow
    \textcolor {darkred}{t_R{<}4} 
%\qquad
%     \{A\}^\star \cdot \{B\}
%    \CONTAIN
%     \{A\}^\star \cdot \{B\}
  }
}

\infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {
      darkred}{\cdots  \wedge  \cdots
%      
%      t_L^1{+}t_L^2{=}t_L{<}3  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge  t_L^1{=}t_R^1
%       \wedge  t_L^2{=}t_R^2
    } \wedge 
     \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     \{A\}^\star \mysharp  t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
  }
}

\infer[dashed]1[{\textcircled{7}\siderule{\codeme{[REOCCUR]}}}]{
  \code{
    \textcolor {
      darkred}{
%t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge       
       t_L^1{=}t_R^1
    } \wedge 
     \cancel{\{A\} \mysharp  t_L^1}  \cdot  \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     \cancel{\{A\} \mysharp  t_R^1}  \cdot  \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
  }
}

\infer[dashed]1[{\textcircled{6}\siderule{\codeme{[UNFOLD]}}}]{
  \code{
    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2} \wedge 
     ( \{A\} \mysharp  t_L^1  \cdot  \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     ( \{A\} \mysharp  t_R^1  \cdot  \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
  }
}

\infer[dashed]1[{\textcircled{5}\siderule{\codeme{[SPLIT]}}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}  
    \quad \textcolor{darklavender}{(\ddagger)}
  }
}
\end{prooftree}}

>>>>

\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear
\usepackage{pifont}% http://ctan.org/pkg/pifont

\usepackage{tikz}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\usepackage{xcolor}
\usepackage[thicklines]{cancel}
\renewcommand{\CancelColor}{\color{lightgray}}

@@

\autoref{tab:Experimental} presents the evaluation results of a microbenchmark. % summary of a lightweight . 
In this experiment, we select 16 \timedL\ programs, and  annotate temporal specifications
with a 1:1 ratio for succeeded/failed cases. 
It records: 
the index of the program, \textbf{No.};
lines of code, \textbf{LOC}; 
effects inference time, \textbf{Infer(ms)}; 
number of valid properties, \textbf{$\mysharp$Prop(\cmark)}; 
average proving time for the valid properties, \textbf{Avg\text{-}Prove(ms)};
number of invalid properties, \textbf{$\mysharp$Prop(\xmark)}; and 
average disproving time for the invalid properties, \textbf{Avg\text{-}Dis(ms)}. 
Times are counted using milliseconds, and the experiment is done on 
a MacBook Pro with a 2.6 GHz 6-Core Intel Core i7 processor.

\begin{table}[!ht]
\caption{\label{tab:Experimental} Experimental Results. }
%\vspace{-1mm}
\centering
\renewcommand{\arraystretch}{1}
\begin{tabular} {c|c|c|c|c |c|c}
\hline
\textbf{No.} & \textbf{LOC} & \textbf{Infer(ms)} & \textbf{$\mysharp$Prop(\cmark)}   
& \textbf{Avg\text{-}Prove(ms)} & \textbf{$\mysharp$Prop(\xmark)}   & \textbf{Avg\text{-}Dis(ms)} \\ \hline\hline
1    &    18    & 0.037&  5     &  0.7634    & 5   &   0.0116   \\ \hline
2    &    33    & 0.145&  5     &  1.3074    & 5   &   0.045    \\ \hline
3    &    55    & 0.34 &  5     &  6.0766    & 5   &   1.1682   \\ \hline
4    &    84    & 0.098&  5     &  3.0678    & 5   &   0.1058   \\ \hline
5    &    110   & 0.191&  7     &  1.7544    & 7   &   0.5031   \\ \hline
6    &    124   & 0.323&  7     &  4.0114    & 7   &   0.3957   \\ \hline
7    &    138   & 0.321&  7     &  3.8399    & 7   &   0.4261   \\ \hline
8    &    163   & 0.594&  7     &  6.1009    & 7   &   1.5019   \\ \hline
9    &    178   & 0.941&  9     &  10.7758   & 9   &   0.5769   \\ \hline
10   &    185   & 1.921&  9     &  13.9332   & 9   &   0.04422  \\ \hline
11   &    202   & 3.434&  9     &  27.4447   & 9   &   0.0561   \\ \hline
12   &    220   & 6.439&  9     &  59.2226   & 9   &   0.745   \\ \hline
13   &    250   & 3.6  &  11    &  29.5766   & 11  &   0.0662  \\ \hline
14   &    261   & 7.552&  11    &  64.2137   & 11  &   0.6121  \\ \hline     
15   &    293   & 14.896& 11   &  115.9795   & 11  &   0.5462   \\ \hline
16   &    304   &  30.889  &  11    & 237.2522    & 11  &  0.07164        \\ \hline            
%\hline
%\textbf{\quad \ \ Total}  & 2546    &  235   &  446.88   &   305.33   \\ \hline
\end{tabular}
%  \vspace{-1mm}
\end{table}

@@

Looking at the second sub-tree, in step \textcircled{5}, \code{t_L} and \code{t_R} are firstly split 
into \code{t_L^1{+}t_L^2} and \code{t_R^1{+}t_R^2}. 
Then in step {\textcircled{6}, 
\code{\{A\} \mysharp  t_L^1} together with \code{\{A\} \mysharp  t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
%, also
%are unified as new constraint \code{t_L^1{=}t_R^1}.
In step {\textcircled{8}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
%one in
%step \code{\textcircled{1}}, 
Hence we apply the rule \code{[REOCCUR]} to prove it with a succeed side constraints entailment: \code{\textcolor {
      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    }\Rightarrow
    \textcolor {darkred}{t_R{<}4} }. 
%Since the structure of terms \code{t_L^2, t_L} and \code{t_R^2, t_R} are isomorphic,
%we will need to unify \code{t_L^2} and \code{t_R^2} in order to get enough
%time constraints. And in step \code{\textcircled{5}} we prove the proposition to
%be true.

@@

\hypo{
  \code{
   % \textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True} \qquad
   % \epsilon \CONTAIN \epsilon
   {\textcircled{4}\siderule{\codeme{[PROVE]}}}
  }
}

\infer[dashed]1[]{
  \code{
    \textcolor {darkred}{True} \wedge \epsilon \CONTAIN
    \textcolor {darkred}{True} \wedge \epsilon
  }
}

\infer[dashed]1[{\textcircled{3}\siderule{\codeme{[Normalisation]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge \cancel{  B  } \CONTAIN
    \textcolor {darkred}{True} \wedge \cancel{ \epsilon \cdot   B  }
  }
}

\infer[dashed]1[{\textcircled{2}\siderule{\codeme{[UNFOLD]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge   B   \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B  
  }
}
\hypo{(\code{II})}

\infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {darkred}{t_L{<}3}  \wedge    A  ^\star \mysharp  t_L  \cdot    B  
    \CONTAIN
    \textcolor {darkred}{t_R{<}4}  \wedge    A  ^\star \mysharp  t_R  \cdot    B  
  }
}

\infer[dashed]2[{\textcircled{1}\siderule{\codeme{[OR\text{-}LHS]}}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge   A  ^\star \mysharp  t_L \cdot   B  
    \vee \textcolor {darkred}{True} \wedge   B   \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B  
  }
}
\end{prooftree}}
\\~\\

\hline \\
\code{(II):}
{\begin{prooftree}
\hypo{
  \code{
    \textcolor {
      darkred}{t_L{<}3 \wedge } \ \textcolor {
        blue}{t_L^1{+}t_L^2{=}t_L \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    } \Rightarrow
    \textcolor {darkred}{t_R{<}4} 
%\qquad
%       A  ^\star \cdot   B  
%    \CONTAIN
%       A  ^\star \cdot   B  
  }
}

\infer[dashed]1[{\textcircled{8}\siderule{\codeme{[REOCCUR]}}}]{
  \code{
    \textcolor {
      darkred}{t_L{<}3} \wedge 
       A  ^\star \mysharp  t_L^2 \cdot   B  
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
       A  ^\star \mysharp  t_R^2 \cdot   B   \quad  \textcolor{darklavender}{(\ddagger)}
  }
}

\infer[dashed]1[{\textcircled{7}\siderule{\codeme{[UNFOLD]}}} \textcolor{blue}{\code{\pi_u :  (t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1)}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge 
     \cancel{  A   \mysharp  t_L^1}  \cdot    A  ^\star \mysharp  t_L^2 \cdot   B  
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     \cancel{  A   \mysharp  t_R^1}  \cdot    A  ^\star \mysharp  t_R^2 \cdot   B  
  }
}

\infer[dashed]1[{\textcircled{6}\siderule{\codeme{[UNFOLD]}}} \textcolor{blue}{\code{\pi_u :  (t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2)}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge 
     (   A   \mysharp  t_L^1  \cdot    A  ^\star \mysharp  t_L^2) \cdot   B  
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     (   A   \mysharp  t_R^1  \cdot    A  ^\star \mysharp  t_R^2) \cdot   B  
  }
}

\infer[dashed]1[{\textcircled{5}\siderule{\codeme{[SPLIT]}}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge   A  ^\star \mysharp  t_L \cdot   B  
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B    
    \quad \textcolor{darklavender}{(\ddagger)}
  }
}
\end{prooftree}}
